Comparing OTU quality across clustering strategies

### 2021-07-17 exploratory/2021/algorithm_diagram.Rmd
Tweak plot annotations

```{r lib}
library(here)
library(tidyverse)
library(diagram)
library(reticulate)
use_python('~/miniconda3/bin/python')
```

@@

```{r ggraph_exp, fig.dim=c(6,5), dpi=300}
plot_graph <- function(graph) {
  create_layout(graph, 'linear', sort.by = id) %>% 
  ggraph() +
  geom_edge_arc(aes(label = mcc,
                    start_cap = label_rect(node1.name),
                    end_cap = label_rect(node2.name)), 
                arrow = arrow(length = unit(4, 'mm'),
                              type = 'closed'),
                edge_colour = 'gray',
                angle_calc = 'along',
                label_dodge = unit(-2, 'mm')
                ) +
  geom_edge_loop(aes(#span = 1, strength = 0.2, direction = 270, 
                     color = is_loop)) +
  geom_node_label(aes(label = name)) +
    scale_edge_color_manual(values = c('black')#c('white')
                            ) +
  theme_void() +
  theme(plot.margin=unit(x=c(0,0,10,0), units="pt"),
        legend.position = 'none')
}

@@

```{r plot_optifit_iters, fig.dim=c(6,5), dpi=300}
lapply(optifit_iters, function(x) {
  tbl_graph(nodes = x$nodes, edges = x$edges) %>% 
    plot_graph()
}) %>% 
  wrap_plots(ncol = 1)
```

>>>>

```{r lib}
library(here)
library(tidyverse)
library(diagram)
library(glue)
library(reticulate)
use_python('~/miniconda3/bin/python')
```

@@

```{r ggraph_exp, fig.dim=c(6,5), dpi=300}
plot_graph <- function(graph, title = '') {
  create_layout(graph, 'linear', sort.by = id) %>% 
  ggraph() +
  geom_edge_arc(aes(label = mcc,
                    start_cap = label_rect(node1.name),
                    end_cap = label_rect(node2.name)), 
                arrow = arrow(length = unit(4, 'mm'),
                              type = 'closed'),
                edge_colour = 'gray',
                angle_calc = 'along',
                label_dodge = unit(-2, 'mm')
                ) +
  geom_edge_loop(aes(span = 1, direction = 90, strength = 0.2,# direction = 270, 
                     color = is_loop)) +
  geom_node_label(aes(label = name)) +
    scale_edge_color_manual(values = c('black')#c('white')
                            ) +
  labs(title = title) +
  theme_void() +
  theme(plot.margin=unit(x=c(0,0,10,0), units="pt"),
        legend.position = 'none')
}

@@

## plot optifit iterations with ggraph & patchwork

```{r plot_optifit_iters, fig.dim=c(6.875,9.0625), dpi=300}
# TODO custom modifications for loop span & direction
lapply(optifit_iters, function(x) {
  tbl_graph(nodes = x$nodes, edges = x$edges) %>% 
    plot_graph(title = glue('mcc = {x$edges %>% filter(is_loop) %>% pull(mcc)}'))
}) %>% 
  wrap_plots(ncol = 1) +
  plot_annotation(tag_levels = 'A')
```
